\newdualentry{ecma}{Ecma}{European association for standardizing information and communication systems}
{The European association for standardizing information and communication systems is a standardisation organisation responsible in particular for the ECMAScript language, \ie JavaScript.}

\newdualentry{http}{HTTP}{HyperText Transfer Protocol}
{The Hypertext Transfer Protocol is an application-level protocol for distributed, collaborative, hypermedia information systems. It is a generic, stateless, protocol which can be used for many tasks beyond its use for hypertext, such as name servers and distributed object management systems, through extension of its request methods, error codes and headers (see RFC2616~\cite{RFC2616}).}
\newdualentry{https}{HTTPS}{HyperText Transfer Protocol Secured}
{HyperText Transfer Protocol Secured (see RFC2818~\cite{RFC2818}).}[http]
\newdualentry{ua}{UA}{User-Agent}
{A User-Agent is an HTTP client.}[http]

\newdualentry{ice}{ICE}{Interactive Connectivity Establishment}
{Internet Connectivity Establishment is a protocol for Network Address Translator (NAT) traversal for UDP-based multimedia sessions established with the offer/answer model. ICE makes use of the Session Traversal Utilities for NAT (STUN) protocol and its extension, Traversal Using Relay NAT (TURN). ICE can be used by any protocol utilizing the offer/answer model, such as the Session Initiation Protocol (SIP) (see RFC5245~\cite{RFC5245}).}
\newdualentry{stun}{STUN}{Session Traversal Utilities for NAT}
{Session Traversal Utilities for NAT is a protocol that serves as a tool for other protocols in dealing with Network Address Translator (NAT) traversal (see RFC5389~\cite{RFC5389}).}[ice]
\newdualentry{turn}{TURN}{Traversal Using Relays around NAT}
{Traversal Using Relays around NAT allows the traversal of NAT router through a TURN server relay (see RFC5766~\cite{RFC5766}).}[ice]
\newdualentry{nat}{NAT}{Network Address Translator}
{A Network Address Translator re-maps an IP address into another by modifying packet headers while in transit. It is usually used to hide an private IP address space into a single public IP address.}[ice]
\newdualentry{ip}{IP}{Internet Protocol}
{The Internet Protocol provides for transmitting blocks of data called datagrams from sources to destinations, where sources and destinations are hosts identified by fixed length addresses (see RFC791~\cite{RFC791}).}
\newdualentry{os}{OS}{Operating System}
{Operating System}
\newdualentry{uri}{URI}{Uniform Resource Identifier}
{A Uniform Resource Identifier is a compact sequence of characters that identifies an abstract or physical resource (see RFC3986~\cite{RFC3986}).}
\newdualentry{url}{URL}{Uniform Resource Locator}
{Uniform Resource Locator (see RFC3986~\cite{RFC3986}).}
\newdualentry{cors}{CORS}{Cross-Origin Resource Sharing}
{Cross-Origin Resource Sharing is a web security mechanism to allow resources on a webpage to be requested from an origin outside of the webpage's origin (see RFC6454~\cite{RFC6454}).}
\newdualentry{csp}{CSP}{Content Security Policy}
{Content Security Policies is a mechanism by which web developers can control the resources which a particular page can fetch or execute, as well as a number of security-relevant policy decisions~\cite{9524886}.}
\newdualentry{rfc}{RFC}{Request For Comments}
{Request For Comments are memorandum published by the Internet Engineering Task Force (IETF).}[ietf]
\newdualentry{ui}{UI}{User Inteface}
{User Inteface}
\newdualentry{sdk}{SDK}{Software Development Kit}
{A Software Development Kit is a set of tools and libraries facilitating the development of applications.}


\newdualentry{ca}{CA}{Certification Authority}
{Certification Authority are responsible for signing and issuing cryptographic certificates.}[tls]
\newdualentry{mitm}{MitM}{Man-in-the-Middle}
{A Man-in-the-Middle attack is a kind of cryptographic attack where the attacker is setup between two communicating parties and secretly intercepts and relays their messages.}
\newdualentry{idp}{IdP}{Identity Provider}
{Identity Provider}
\newdualentry{cs}{CS}{Communication Service}
{Communication Service}
\newdualentry{voip}{VoIP}{Voice over IP}
{Voice over IP designates the techniques to communicate using voice or voice and video over any compatible IP networks.}
\newdualentry{spit}{SPIT}{SPam over Internet Telephony}
{SPam over Internet Telephony}
\newdualentry{sso}{SSO}{Single Sign-On}
{Single Sign-On systems permit users to log in with a single identifier and password to access a set of systems.}
\newdualentry{aal}{AAL}{Authentication Assurance Levels}
{Authentication Assurance Level}
\newdualentry{rp}{RP}{Relying Party}
{A Relying Party is an OAuth~2 client using OpenID Connect.}[oauth2]
\newdualentry{oidc}{OIDC}{OpenID Connect}
{OpenID Connect 1.0 is a simple identity layer on top of the OAuth 2.0 protocol~\cite{sakimura_openid_2014}.}[oauth2]
\newdualentry{ro}{RO}{Resource Owner}
{Resource Owner (OAuth~2 role)}[oauth2]
\newdualentry{rs}{RS}{Resource Server}
{Resource Server (OAuth~2 role)}[oauth2]
\newdualentry{as}{AS}{Authorization Server}
{Authorization Server (OAuth~2 role)}[oauth2]
\newdualentry{oauth2}{OAuth~2}{OAuth~2}
{The OAuth~2 authorization framework enables a third-party application to obtain limited access to an HTTP service on behalf of a resource owner (see RFC6749~\cite{RFC6749}).}[oauth2]
\newdualentry{acr}{ACR}{Authentication Context Class Reference}
{Authentication Context Class Reference (OIDC claim)}[oauth2]


\newdualentry{acor}{ACOR}{Authentication Class and Origin Request}
{Authentication Class and Origin Request is our proposed extension to SDP for the negotiation of identity parameters.}
\newdualentry{acrus}{ACR}{Authentication Class Request}
{Authentication Class Request is a parameter of out ACOR extension to SDP.}[acor]
\newdualentry{orus}{OR}{Origin Request}
{Origin Request is a parameter of our ACOR extension to SDP.}[acor]



\newdualentry{tcb}{TCB}{Trusted Computing Base}
{Trusted Computing Base}
\newdualentry{sdp}{SDP}{Session Description Protocol}
{Session Description Protocol is intended for describing multimedia sessions for the purposes of session announcement, session invitation, and other forms of multimedia session initiation (see RFC4566~\cite{RFC4566}).}


\newdualentry{lte}{LTE}{Long Term Evolution}
{The Long Term Evolution mobile network is a standard for high-speed mobile networks designed by the 3GPP.}
\newdualentry{volte}{VoLTE}{Voice over LTE}
{Voice over LTE is an architecture for VoIP over 4G mobile networks.}[lte]
\newdualentry{ue}{UE}{User Equipement}
{User Equipement (LTE role)}[lte]
\newdualentry{ims}{IMS}{IP Multimedia Subsystem}
{The IP Multimedia Subsystem aims at merging telecommunication technologies under an all-IP environment.}
\newdualentry{qos}{QoS}{Quality of Service}
{Quality of Service is the description or measurement of the performance of a service, in particular as seen by the user.}
\newdualentry{uicc}{UICC}{Universal Integrated Circuit Card}
{The Universal Integrated Circuit Card is a smart card used for mobile phones authentication and security, often referred as the SIM card.}


\newdualentry{ott}{OTT}{Over The Top}
{Over The Top services are provided on top of existing internet service providers networks.}
\newdualentry{api}{API}{Application Programming Interface}
{An Application Programming Interface is a particular set of rules and specifications that a software program can follow to access and make use of the services and resources provided by another particular software program that implements that API.}

\newdualentry{p2p}{P2P}{Peer-to-Peer}
{Peer-to-Peer}
\newdualentry{osn}{OSN}{Online Social Network}
{An Online Social Network is a platform where users build social relations based on personal or professional interests.}
\newdualentry{cdn}{CDN}{Content Delivery Network}
{A Content Delivery Network is constituted of proxy servers geographically distributed to be as close to clients as possible in order to transparently provide high availability and performance.}


\newdualentry{ietf}{IETF}{Internet Engineering Task Force}
{The Internet Engineering Task Force (IETF) is the premier Internet standards body, developing open standards through open processes.}
\newdualentry{w3c}{W3C}{World Wide Web Consortium}
{The World Wide Web Consortium (W3C) is an international community where Member organizations, a full-time staff, and the public work together to develop Web standards.}
\newdualentry{arcep}{ARCEP}{Regulation Authority for Postal and Electronic Communications}
{Autorité de Régulation des Communications Électroniques et des Postes is the French regulation authority for postal and electronic communications.}
\newdualentry{gdpr}{GDPR}{General Data Protection Regulation}
{The General Data Protection is an European Union regulation on the protection of natural persons with regard to the processing of personal data and on the free movement of such data.}
\newdualentry{eu}{EU}{European Union}
{European Union.}
\newdualentry{3gpp}{3GPP}{3rd Generation Partnership Project}
{The 3rd Generation Partnership Project is a cooperation organisation between telecommunication standard organisations.}
\newdualentry{cve}{CVE}{Common Vulnerabilities and Exposure}
{The Common Vulnerabilities and Exposure database references public security vulnerabilities.}




\newdualentry{dos}{DoS}{Denial of Service}
{A Denial of Service attack targets the availability of a machine or network, usually by flooding the target with illegitimate requests.}
\newdualentry{ddos}{DDoS}{Distributed Denial of Service}
{Distributed Denial of Service}[dos]

\newdualentry{jwt}{JWT}{JSON Web Token}
{JSON Web Token is a compact, URL-safe means of representing claims to be transferred between two parties. The claims in a JWT are encoded as a JSON object that is used as the payload of a JSON Web Signature (JWS) structure or as the plaintext of a JSON Web Encryption (JWE) structure, enabling the claims to be digitally signed or integrity protected with a Message Authentication Code (MAC) and/or encrypted (see RFC7519~\cite{RFC7519}).}
\newdualentry{jws}{JWS}{JSON Web Token Signature}
{JSON Web Token Signature}[jwt]
\newdualentry{jwe}{JWE}{JSON Web Token Encryption}
{JSON Web Token Encryption}[jwt]
\newdualentry{jose}{JOSE}{JavaScript Object Signing and Encryption}
{JavaScript Object Signing and Encryption}[jwt]
\newdualentry{json}{JSON}{JavaScript Object Notation}
{JavaScript Object Notation is a lightweight, text-based, language-independent data interchange format derived from the ECMAScript (see RFC7159~\cite{RFC7159}).}
\newdualentry{jku}{JKU}{JSON Key URL}
{JSON Key URL (a JWT header parameter).}[jwt]


\newdualentry{sip}{SIP}{Session Initiation Protocol}
{The Session Initiation Protocol is an application-layer control (signaling) protocol for creating, modifying, and terminating sessions with one or more participants. These sessions include Internet telephone calls, multimedia distribution, and multimedia conferences (see RFC3261~\cite{RFC3261}).}
\newdualentry{csrf}{CSRF}{Cross-Site Request Forgery}
{Cross-Site Request Forgery is a type of vulnerability allowing an attacker to issue unauthorized commands in name of the user.}
\newdualentry{jsep}{JSEP}{JavaScript Session Establishment Protocol}
{JavaScript Session Establishment Protocol allows a JavaScript application to control the signaling plane of a multimedia session via the interface specified in the W3C RTCPeerConnection API, and discusses how this relates to existing signaling protocols~\cite{I-D.ietf-rtcweb-jsep}.}
\newdualentry{cscf}{CSCF}{Call Session Control Function}
{Call Session Control Function}
\newdualentry{xss}{XSS}{Cross-Site Scripting}
{Cross-Site Scripting is a vulnerability of web applications allowing an attacker to inject malicious scripts from a domain into another. }
\newdualentry{voipsa}{VoIPSA}{VoIP Security Alliance}
{The VoIP Security Alliance aims to fill the void of VoIP security related resources through a unique collaboration of VoIP and Information Security vendors, providers, and thought leaders.}
\newdualentry{vpn}{VPN}{Virtual Private Network}
{A Virtual Private Network extends a private network through a public network, often over a secure tunnel established with TLS.}
\newdualentry{vbr}{VBR}{Variable Bit-Rate}
{Variable Bit-Rate files vary the amount of output data per time segment, as opposed to constant bit-rate.}
\newdualentry{acme}{ACME}{Automatic Certificate Management Environment}
{The Automatic Certificate Management Environment is a protocol that a certification authority (CA) and an applicant can use to automate the process of verification and certificate issuance~\cite{I-D.ietf-acme-acme}.}
\newdualentry{udp}{UDP}{User Datagram Protocol}
{The User Datagram Protocol provides a procedure for application programs to send messages to other programs with a minimum of protocol mechanism. The protocol is transaction oriented, and delivery and duplicate protection are not guaranteed (see RFC768~\cite{RFC768}).}
\newdualentry{tcp}{TCP}{Transmission Control Protocol}
{The Transmission Control Protocol (TCP) is intended for use as a highly reliable host-to-host protocol between hosts in packet-switched computer communication networks, and in interconnected systems of such networks (see RFC793~\cite{RFC793}.}
\newdualentry{tls}{TLS}{Transport Layer Security}
{Transport Layer Security provides communications security over the Internet. The protocol allows client/server applications to communicate in a way that is designed to prevent eavesdropping, tampering, or message forgery (see RFC5246~\cite{RFC5246}).}
\newdualentry{dtls}{DTLS}{Datagram Transport Layer Security}
{The DTLS protocol provides communications privacy for datagram protocols. The protocol allows client/server applications to communicate in a way that is designed to prevent
 eavesdropping, tampering, or message forgery. The DTLS protocol is based on the Transport Layer Security (TLS) protocol and provides equivalent security guarantees. Datagram semantics of the underlying transport are preserved by the DTLS protocol (see RFC6347~\cite{RFC6347}).}
\newdualentry{srtp}{SRTP}{Secure Real-time Transport Protocol}
{The Secure Real-time Transport Protocol is a secure profile for the RTP protocol (see RFC3711~\cite{RFC3711}).}[rtp]
\newdualentry{rtp}{RTP}{Real-time Transport Protocol}
{The Real-time Transport Protocol provides end-to-end network transport functions suitable for applications transmitting real-time data, such as audio, video or simulation data, over multicast or unicast network services (see RFC3550~\cite{RFC3550}).}
\newdualentry{rtcp}{RTCP}{RTP Control Protocol}
{The RTP Control Protocol is a protocol for controlling RTP sessions (see RFC3550~\cite{RFC3550}).}[rtp]
\newdualentry{dtlssrtp}{SRTP profile for DTLS}{DTLS-SRTP}
{is an extension of the Datagram Transport Layer Security (DTLS) protocol to establish keys for Secure Real-time Transport Protocol (SRTP) (see RFC5763~\cite{RFC5763}).}[dtls]
\newdualentry{sctp}{SCTP}{Stream Control Transmission Protocol}
{The Stream Control Transmission Protocol is designed to transport Public Switched Telephone Network (PSTN) signalling messages over IP networks, but is capable of broader applications (see RFC4960~\cite{RFC4960}).}
\newdualentry{sdes}{SDES}{Session Description Protocol Security Descriptions}
{The Session Description Protocol Security Descriptions serves to configure security for a unicast media stream in either a single message or a roundtrip exchange (see RFC4568~\cite{RFC4568}).}



\newdualentry{aaa}{AAA}{Authentication, Authorization, and Accounting}
{Authentication, Authorization, and Accounting}
\newdualentry{sas}{SAS}{Short Authentication String}
{Short Authentication String}
\newdualentry{dht}{DHT}{Distributed Hash Table}
{A Distributed Hash Table is a distributed storage infrastructure providing a key/value lookup functionality.}
\newdualentry{guid}{GUID}{Globally Unique IDentifier}
{Globally Unique IDentifier (reThink project)}


\newdualentry{posix}{POSIX}{Portable Operating System Interface}
{The Portable Operating System Interface is a set of standards of compatibility between operating systems.}

